% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage{hyperref}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{Johannes Mauritzen}

\address{Institutt for industriell \o konomi og teknologiledelse\\ NTNU\\
7491 Trondheim \\ mob:  +47 90 56 64 62 \\ email: johannes.mauritzen@nhh.no \\
website:  \url{jmaurit.github.io} }
                           
                        
\begin{resume} 
\section{PERSONAL}
\begin{itemize} 
\item[] Born July 21, 1982
\item[] Norwegian Citizen

\normalsize{\section{Languages}}
\item[] Norwegian and English: Native
\item[] German: Beginner 

\normalsize{\section{Fields of interest}}
\item[] Energy Economics, Business Economics, Natural Resource and Environmental Economics, Applied Statistics/Econometrics, Industrial Organisation
\end{itemize}  


\section{PUBLICATIONS}       

\normalsize{\section{Peer Reviewed}}
\begin{itemize}
\setlength{\itemsep}{10pt}
\item[] \emph{How electricity price spikes can help overcome the energy efficiency gap}\\
Economics Letters, Vol. 134, September 2015, Pages 114-117.

\item[] \emph{Now or Later? Trading wind power closer to real-time and how poorly designed subsidies lead to higher balancing costs}\\
The Energy Journal, Vol. 36, No. 4, 2015 

\item[] \emph{The Decision to Scrap a Wind Turbine: Policy changes, scrapping incentives and why wind turbines in good locations get scrapped first}\\
The Energy Journal, Vol. 35, No. 2, 2014.

\item[] \emph{Dead Battery? Wind Power, the Spot Market, and Hydropower Interaction in the Nordic Electricity Market}\\
The Energy Journal, Vol. 34, No. 1, 2013
\end{itemize}

\normalsize{\section{Conference Proceedings}}
\begin{itemize}  
\setlength{\itemsep}{10pt}
\item[] \emph{What Happens When it's Windy in Denmark? How Wind Power Affects Price Variability in the Nordic Electricity Market}\\ 
International Association for Energy Economics International Conference, Stockholm 2011  \\
Student Paper Award Recipient 
\end{itemize}

\normalsize{\section{Working Papers}}
\begin{itemize}  
\setlength{\itemsep}{10pt}
\item[] \emph{Real-time Versus Day-ahead Market Power in a Hydro-based Electricity Market} \\ 
With Thomas Tanger\aa s, Research Institute of Industrial Economics.
\item[] \emph{The Effect of Oil Prices on Offshore Production: Evidence from the Norwegian Continental Shelf}
\item[] \emph {Sun and Lemons: Getting over Information Asymmetries in the California Solar Market} \\
Presented at Allied Social Sciences Associations Conference in Boston, January 2015 \\
\end{itemize}

\section{REPORTS AND ANALYSIS} 
\begin{itemize} 
\setlength{\itemsep}{5pt}
\item[] \href{http://klimastiftelsen.no/wp-content/uploads/2015/06/NK5_2015_Solenergirevolusjonen.pdf}{\emph{En verden med billig solkraft} Hva betyr solenergirevolusjonen, Norsk Klimastiftelsen nr 5/2015} 
\end{itemize}

\section{PUBLICATIONS IN POPULAR PRESS} 
\begin{itemize} 
\setlength{\itemsep}{5pt}
\item[] \href{http://www.ft.com/intl/cms/s/0/e22cba5c-1bfa-11e5-a130-2e7db721f996.html#axzz3giRBkRau}{\emph{An outdated view of wind turbines.}} Financial Times, letters, July 3rd, 2015.
\item[] \href{http://www.ft.com/intl/cms/s/0/313360bc-a00c-11e4-aa89-00144feab7de.html#axzz3PVKMfhY5}{\emph{The attractiveness of electric cars has little to do with the price of oil.}} Financial Times, letters, January 21st, 2015.
\item[] \href{http://www.economist.com/news/letters/21595871-livestock-and-emissions-california-technology-and-jobs-algorithms}{\emph{Technology, jobs and urbanisation.}}   The Economist, letters, February 8th, 2014.
\item[] \href{http://www.economist.com/news/letters/21571848-nordic-countries-private-schools-immigration-sandhurst-ed-koch-richard-iii}{\emph{Too generous to Norway.}} The Economist, letters, February 16th, 2013.
\item[] \href{http://www.ft.com/intl/cms/s/0/26168da6-238d-11e2-bb86-00144feabdc0.html#axzz2sclP2DP5}{\emph{Electric cars are being mass-produced.}}  Financial Times, letters, November 5th, 2012.
\item[] \href{http://www.ft.com/intl/cms/s/0/553d8cf6-fb56-11e1-87ae-00144feabdc0.html#axzz2sclP2DP5}{\emph{Europe should let China subsidize its energy production.}}  Financial Times, Letters, September 11th, 2012.


\normalsize{\section{In Norwegian}}
\item[] \href{http://www.e-pages.dk/bergenstidende/1809/article/264899/28/2/render/?token=02cd272aa0579373983f0bf8c4cee611}{ \emph{K\o prising skal gjøre vondt}} Bergens Tidende, April 27th 2015
\item[] \href{http://www.bt.no/meninger/debatt/Derfor-faller-oljeprisen-3282375.html}{ \emph {Derfor faller oljeprisen} Bergens Tidende, January 19th, 2015}
\item[] \href{http://www.e-pages.dk/bergenstidende/1700/article/227941/31/4/render/?token=5207fb9bf5f917b5276532ef05164266}{ \emph {Billig Klimaforsikring} Bergens Tidende, January 6th, 2015}
\item[] \href{http://www.bt.no/meninger/debatt/Mytene-om-hoye-bygg-3234980.html}{ \emph {Mytene om h\o ye bygg} Bergens Tidende, November 6th, 2014}
\item[] \href{http://www.bt.no/meninger/debatt/Den-absurde-skattepolitikken-3191273.html}{\emph{Den absurde skattepolitikken} Bergens Tidende, September 8th, 2014}
\item[] \emph {Sykkelpartiet H\o yre}  Bergens Tidende, August 4th, 2014.
\item[] \emph {Dyr symbolpolitikk}  Bergens Tidende, June 7th, 2014.
\item[] \emph {En lysere sykkelfremtid}  Bergens Tidende, May 7th, 2014.
\item[] \emph {Rene investerings}  Bergens Tidende, April 5th, 2014.
\item[] \href{http://www.nhh.no/Files/Filer/institutter/for/bedriftsøkonomisk_debatt/2013/mauritzen-livet_etter_oljen-bt-310713.pdf}{\emph {Livet etter oljen}  Bergens Tidende, July 31st, 2013.}
\item[] \emph {Bevar Bryggen, Bygg Bybanen}  Bergens Tidende, March 30th, 2013.
\item[] \emph {Norge er sykkelversting i Nord-Europa} Aftenposten, September 20th, 2012.
\item[] \emph {Bygg H\o yere!, Aftenposten} August 10th, 2012.
\end{itemize}

\section{PRESENTATIONS}      
 
\begin{itemize}
\normalsize{\section{2015}} 
\item[] ASSA Boston, FIBE, UCL Department of Statistics, NTNU Department of Industrial Economics, University of Stavanger Business School, University of Aberdeen, RWTH Aachen.
\normalsize{\section{2014}} 
\item[] IAEE New York, IAEE Asia Conference - Beijing, Research Institute of Industrial Economics (Stockholm), Norwegian Conference for Business Economics (FIBE),Workshop on Intermittent Renewables and Market Design - Hardanger, Economics of Uncertainty Workshop - NTNU, CenSES Annual Conference, University of Neuchatel  
\normalsize{\section{2013}}
\item[] IAEE Dusseldorf, Research Institute of Industrial Economics, FIBE, CenSES Annual Conference 
\normalsize{\section{2012}}
\item[] NTNU Department of Industrial Economics, University of Southern Denmark - Esbjerg, Swedish Department of Commerce - Energy Division
\end{itemize}

 
\section{RESEARCH AND WORK EXPERIENCE}      
					    % is 3 inches wide
                  \begin{itemize}
                  \setlength{\itemsep}{10pt}
                  \item[] Visiting researcher, Department of Industrial Economics and Technology Management, Norwegian University of Science and Technology. \\ August 2015 - present. 
                  \item[] Post-doctoral Fellow, Center for Sustainable Energy Studies, Norwegian School of Economics, Department of Business and Management Science. \\ January 2013 - present.

                  \item[] Visiting researcher, Department of Statistical Science, University College London. \\ February - March, 2015
                  
                  \item[] Research Institute of Industrial Economics (IFN), Stockholm, Sweden.
                    \begin{itemize} 
                    \item[] Affiliated Researcher, January 2013 to present.
                    \item[] Research Fellow, May 2012 to December 2012.
                    \item[] Guest Researcher, September to 2011 to May 2012.
                    \end{itemize}
                  \item[] Research Scholar, NHH Norwegian School of Economics, Department of Finance and Management Science. August 2008 to August 2012.  
                  Research towards Ph.D. degree.  25\% teaching.
                  
                  \item[] Graduate Research Assistant, Center for Reinventing Public Education, University of Washington, Seattle, WA. June 2007 to August 2008.  
                  Cleaning and analyzing longitudinal data sets related to research on charter schools.  Extensive work with Stata and statistical modeling.  Some field work / interviewing.
                  
                  \item[] Research Analyst, Levy Forecasting Center, LLC, Mount Kisco, NY. July 2004 to June 2006.  
                  Researched macroeconomics trends in finance, capital spending, and inventories. Aided in calculating forecasts. Wrote analytical piece in monthly newsletter. Aided in drafting memos and bulletins to clients. Designed and implemented forecasting tool using Visual Basic. 

                  \end{itemize}
                   
\section{TEACHING} 
\begin{itemize}
\setlength{\itemsep}{10pt}
\item[] Lecturer, Bergen Summer Research School, University of Bergen.  Getting started with energy and climate data analysis with R.  Summer 2014.
\item[] Guest Lecturer, Environmental Economics, NHH.  Non-market valuation and using the R statistical programming language.  Spring 2013 and spring 2014.
\item[] Lecturer, Physics and Economics of Renewable Energy (with Jan Petter Hansen, University of Bergen), NHH.  Spring 2010 and spring 2011.
\item[] Teaching Assistant: Driftsregnskap og Budsjettering (Introduction to Management Accounting and Budgeting.)
\item[] Teaching Assistant: Introduction to Microeconomics, Introduction to Macroeconomics.  University of Washington, Department of Economics. Fall 2006, Spring 2007.
\item[] Norwegian Instructor, high school credit course.  Concordia Language Villages, Bemidji MN.  Summer 2006.  
\item [] Masters thesis supervision:
  \begin{itemize}
  \item[] Emma Micklem, NHH. \emph{Wind Power in South Africa.}
  \item[] Christopher Brenner, NHH. \emph{Biomass and the German Energy Policy.}
  \item[] Louis Magnus Pauchon, NHH. \emph{Energy Efficiency Policy for Buildings: A comparison of Norway and France.}
  \item[] Arild Huitfeldt og Torgeir Persen, NHH.  \emph{Realopsjonsanalyse av Vindkraftverk under utvikling – Vil en realopsjonstiln\ae rming forbedre verdivurderingen av et vindkraftverk under utvikling? (Will a Real-Options Approach Improve the Valuation of a Wind Park under Development?)}
  \item[] Kjartan Skj\ae veland and T\o nnes Thompson, NHH. \emph{The End of a Long Term Relationship between the Price of Crude Oil and Natural Gas: A Cointegration Approach.} 
  \item[] Arve Tundal and Mari Hougsn\ae s, NHH.  \emph{Kostnadsanalyse: Hydro Aluminium Sunndal.  En vurdering av fremtidig anodeleverand\o r til Hydro Aluminium Sunndal. (A Valuation of Future Anode Deliveries to Hydro Aluminium Sunndal.)} 
  \item[] Nikolaos Tsagkaropoulos, NHH. \emph{Bicycle Sharing Systems, Are They Here To Stay?} Fall 2014
  \item[] Ivan Paladin and Kenza Taoufik, NHH. \emph{The Cost of Sun: The Case Study of Croatia using a Levelized Cost of Energy Approach.}
  \end{itemize}
\end{itemize}

\section{EDUCATION}      
 
\begin{itemize}
\normalsize{\section{Ph.D. Business Economics \\ August 2008 - May 2012}} 
\item[] Department of Finance and Management Science\\
NHH Norwegian School of Economics \\
Bergen, Norway \\   

\normalsize{\section{\bf Master of Arts \\ August 2006 - June 2008}}
\item[] Department of Economics \\
University of Washington \\
Seattle, WA, USA \\

\normalsize{\section{\bf Bachelor of Arts \\ August 2000 - May 2004}}
\item[] St. Olaf College  \\
Mathematics and History Majors \\
Summe Cum Laude \\
Northfield, MN, USA \\
\end{itemize}

\section{REFEREEING}  
\begin{itemize}
\item[] Journal of Environmental Economics and Management, The Energy Journal, Energy Economics, Journal of Energy Engineering, Journal of Sustainable Energy Planning and Management
 \end{itemize}

\section{PROGRAMMING}
\begin{itemize}
  \item[] R, Python, html/css, Stata, some Matlab, C++, Visual Basic
\end{itemize}

\section{PEDAGOGICAL TRAINING}
\begin{itemize}
\setlength{\itemsep}{10pt}
\item[] Teaching Economics, credit course, Fall 2006, Department of Economics, University of Washington, Seattle (with Eugene Silberberg)

\item[] Pedagogical Training Certificate, Spring 2013, NHH, (with Arild Raaheim, University of Bergen/NHH)
\end{itemize}

\section{OTHER RELEVANT ACTIVITIES}
\begin{itemize}
\setlength{\itemsep}{10pt}
\item[] Organized NHH Business and Management Science Seminar series, Spring 2013 to Fall 2014
\item[] Organized NHH Finance and Management Science Internal Seminar, Fall 2009 to Spring 2011, Spring 2013 to Spring 2014
\item[] NHH Finance and Management Science Department Board Representative, Fall 2009 to Spring 2011 and Fall 2013 to Spring 2014
\item[] NHH Ph.D. Program Board Student Representative, Fall 2010 to Spring 2011
\item[] Blogger: \url{jmaurit.github.io#blog} and \url{reconhub.com}
\end{itemize}
 
\section{REFERENCES}
\begin{itemize}
\setlength{\itemsep}{10pt}
\item[] Jonas Andersson \\
Professor of Statistics \\
Department of Business and Management Science\\
NHH Norwegian School of Economics \\
email: jonas.anderson@nhh.no\\
tel: +47 55 95 96 81\\
fax: +47 55 95 47\\

\item[] Afzal Siddiqui \\
Senior Lecturer \\
Department of Statistical Science\\
University College London \\
email: afzal.siddiqui@ucl.ac.uk\\
tel: +44(0)20 7679 1871\\

\item[] Harrison Fell \\
Assistant Professor \\
Division of Economics and Business \\
Colorado School of Mines\\
email: hfell@mines.edu\\
tel: +1 303 273 3757\\
fax: +1 303 273 3416\\

\end{itemize}

\end{resume} 
\end{document}









