% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage{hyperref}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{Johannes Mauritzen}

\address{ mob:  +47 90 56 64 62 \\ email: jmaurit@gmail.com \\
website:  \url{jmaurit.github.io} }
                           
                        
\begin{resume} 

\section{PERSONAL}
\begin{itemize} 
\item[] Born July 21, 1982
\item[] Norwegian Citizen
\end{itemize}

\section{RESEARCH AND WORK EXPERIENCE}      
					    % is 3 inches wide
                  \begin{itemize}
                  \setlength{\itemsep}{10pt}
                  \item[] Associate Professor, BI Norwegian School of Business, Campus Trondheim. \\From March 2016
                  \item[] Postdoctor, Department of Industrial Economics and Technology Management, Norwegian University of Science and Technology. \\ August 2015 - March 2016. 
                  \item[] Postdoctor in Energy and Environmental Economics, Center for Sustainable Energy Studies, Norwegian School of Economics, Department of Business and Management Science. \\ January 2013 - December 2015.

                  
                  \item[]Research Institute of Industrial Economics (IFN), Stockholm, Sweden. \\ September 2011 - December 2012. 
                  
                  \item[] Research Scholar, NHH Norwegian School of Economics, Department of Finance and Management Science. August 2008 to August 2012.  
                  \end{itemize}
                   

\section{COURSES TAUGHT}
\begin{itemize}
\item[] Environmental Economics, Economics of Renewable Energy, Microeconomics, Project Management
\end{itemize}

\section{ACADEMIC PUBLICATIONS}
\begin{itemize}
\item[] The Energy Journal, Economics Letters. 
\end{itemize}

\section{POPULAR PUBLICATIONS}
\begin{itemize}
\item[] The Economist, Financial Times, Sysla Gr\oe nn, Dagens Næringsliv, Bergens Tidende, Aftenposten. 
\end{itemize}

\section{EDUCATION}      
 
\begin{itemize}
\normalsize{\section{Ph.D. Management Science \\ August 2008 - May 2012}} 
\item[] Department of Finance and Management Science\\
NHH Norwegian School of Economics \\
Bergen, Norway \\   

\normalsize{\section{\bf Master of Arts \\ August 2006 - June 2008}}
\item[] Department of Economics \\
University of Washington \\
Seattle, WA, USA \\

\normalsize{\section{\bf Bachelor of Arts \\ August 2000 - May 2004}}
\item[] St. Olaf College  \\
Mathematics and History Majors \\
Summe Cum Laude \\
Northfield, MN, USA \\
\end{itemize}


\end{resume} 

\end{document}









